Reinforcement Learning Produces Dominant Strategies for the Iterated Prisoner's Dilemma

### 2017-11-03 plos/main.tex
Make minor adjustments requested by PLOS.

% Header and Footer with logo
\usepackage{lastpage,fancyhdr}
\usepackage[draft]{graphicx}
\usepackage{epstopdf}
\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
\setlength{\headheight}{27.023pt}
\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\sf PLOS}

@@

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline
{ Reinforcement Learning Produces Dominant Strategies for the Iterated Prisoner's Dilemma }
% Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Marc Harper\textsuperscript{1\Yinyang},
Vincent Knight\textsuperscript{2*\Yinyang},
Martin Jones\textsuperscript{3\ddag},
Georgios Koutsovoulos\textsuperscript{4\ddag},
Nikoleta E. Glynatsi\textsuperscript{2\ddag},
Owen Campbell\textsuperscript{3\ddag},
\\
\bigskip
\textbf{1} Affiliation Google Inc., Mountain View, CA, USA
\\
\textbf{2} Affiliation Cardiff University, School of Mathematics, UK
\\
\textbf{3} Not affiliated
\\
\textbf{4} INRA, Université Côte d‘Azur, CNRS, ISA, France
\\
\bigskip

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=.7\textwidth]{lookerup.eps}
    \caption{\bf Diagrammatic representation of the Looker up Archetype.}
    \label{fig:lookerup}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=.7\textwidth]{gambler.eps}
    \caption{\bf Diagrammatic representation of the Gambler Archetype.}
    \label{fig:gambler}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=.9\textwidth]{ann.eps}
    \caption{\bf Diagrammatic representation of the ANN Archetype.}
    \label{fig:ann}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{fsm.eps}
    \caption{\bf Diagrammatic representation of the Finite State Machine Archetype.}
    \label{fig:fsm}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
        \includegraphics[width=.5\textwidth]{FSM16.eps}
        \caption{\bf Evolved\_FSM\_16: trained to maximize score in a standard
        tournament}
        \label{fig:fsm16}
\end{figure}

\begin{figure}
        \centering
        \includegraphics[width=.5\textwidth]{FSM16noise.eps}
        \caption{\bf Evolved\_FSM\_16\_Noise\_05: trained to maximize score in a
        noisy tournament}
        \label{fig:fsm16noise}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{hmm.eps}
    \caption{\bf Diagrammatic representation of the Hidden Markov Model Archetype.}
    \label{fig:hmm}
\end{figure}

@@

\begin{figure}[!hbtp]
        \centering
        \includegraphics[width=.5\textwidth]{standard_tft_scores.eps}
        \caption{\bf Scores for Tit for Tat over
        50000 tournaments.}
        \label{fig:tit_for_tat_scores}
\end{figure}

\begin{figure}[!hbtp]
        \centering
        \includegraphics[width=.5\textwidth]{standard_tft_ranks.eps}
        \caption{\bf Ranks for Tit for Tat over
        50000 tournaments.}
        \label{fig:tit_for_tat_ranks}
\end{figure}

\begin{figure}[!hbtp]
        \centering
        \includegraphics[width=.5\textwidth]{standard_tft_wins.eps}
        \caption{\bf Wins for Tit for Tat over
        50000 tournaments.}
        \label{fig:tit_for_tat_wins}
\end{figure}

@@

\begin{table}[!hbtp]
        \centering
        \footnotesize
\begin{tabular}{lrrrrrrrrr}
\toprule
{} &   mean &    std &    min &     5\% &    25\% &    50\% &    75\% &    95\% &    max \\
\midrule
EvolvedLookerUp2\_2\_2$^{*}$    &  2.955 &  0.010 &  2.915 &  2.937 &  2.948 &  2.956 &  2.963 &  2.971 &  2.989 \\
Evolved HMM 5$^{*}$           &  2.954 &  0.014 &  2.903 &  2.931 &  2.945 &  2.954 &  2.964 &  2.977 &  3.007 \\
Evolved FSM 16$^{*}$          &  2.952 &  0.013 &  2.900 &  2.930 &  2.943 &  2.953 &  2.962 &  2.973 &  2.993 \\
PSO Gambler 2\_2\_2$^{*}$       &  2.938 &  0.013 &  2.884 &  2.914 &  2.930 &  2.940 &  2.948 &  2.957 &  2.972 \\
Evolved FSM 16 Noise 05$^{*}$ &  2.919 &  0.013 &  2.874 &  2.898 &  2.910 &  2.919 &  2.928 &  2.939 &  2.965 \\
PSO Gambler 1\_1\_1$^{*}$       &  2.912 &  0.023 &  2.805 &  2.874 &  2.896 &  2.912 &  2.928 &  2.950 &  3.012 \\
Evolved ANN 5$^{*}$           &  2.912 &  0.010 &  2.871 &  2.894 &  2.905 &  2.912 &  2.919 &  2.928 &  2.945 \\
Evolved FSM 4$^{*}$           &  2.910 &  0.012 &  2.867 &  2.889 &  2.901 &  2.910 &  2.918 &  2.929 &  2.943 \\
Evolved ANN$^{*}$             &  2.907 &  0.010 &  2.865 &  2.890 &  2.900 &  2.908 &  2.914 &  2.923 &  2.942 \\
PSO Gambler Mem1$^{*}$        &  2.901 &  0.025 &  2.783 &  2.858 &  2.884 &  2.901 &  2.919 &  2.942 &  2.994 \\
Evolved ANN 5 Noise 05$^{*}$  &  2.864 &  0.008 &  2.830 &  2.850 &  2.858 &  2.865 &  2.870 &  2.877 &  2.891 \\
DBS                           &  2.857 &  0.009 &  2.823 &  2.842 &  2.851 &  2.857 &  2.863 &  2.872 &  2.899 \\
Winner12                      &  2.849 &  0.008 &  2.820 &  2.836 &  2.844 &  2.850 &  2.855 &  2.862 &  2.874 \\
Fool Me Once                  &  2.844 &  0.008 &  2.818 &  2.830 &  2.838 &  2.844 &  2.850 &  2.857 &  2.882 \\
Omega TFT: 3, 8               &  2.841 &  0.011 &  2.800 &  2.822 &  2.833 &  2.841 &  2.849 &  2.859 &  2.882 \\
\bottomrule
\end{tabular}
        \caption{\bf Standard Tournament: Mean score per turn of top 15 strategies
            (ranked by median over 50000 tournaments).
        The leaderboard is dominated by the trained strategies (indicated by a
        $^{*}$).}
        \label{tbl:standard_score}
\end{table}

@@

\begin{landscape}
    \begin{figure}[!hbtp]
        \centering
        \includegraphics[width=\paperwidth]{standard_scores_boxplots.eps}
        \caption{\bf Standard Tournament: Mean score per turn 
            (strategies ordered by median score over 50000 tournaments).}
        \label{fig:standard_boxplot}
    \end{figure}
\end{landscape}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{standard_scores_heatmap.eps}
    \caption{\bf Standard Tournament: Mean score per turn of row players against
    column players (ranked by median over 50000 tournaments).}
    \label{fig:standard_heatmap}
\end{figure}

@@

\begin{table}[!hbtp]
    \centering
        \caption{\bf Standard Tournament: Number of wins per tournament
        of top 15 strategies (ranked by median wins over
        50000 tournaments).}
        \label{tbl:standard_wins_top_winners}
\begin{tabular}{lrrrrrrrrr}
\toprule
{} &     mean &    std &  min &     5\% &    25\% &    50\% &    75\% &    95\% &  max \\
\midrule
Aggravater          &  161.595 &  0.862 &  160 &  160.0 &  161.0 &  162.0 &  162.0 &  163.0 &  163 \\
Defector            &  161.605 &  0.864 &  160 &  160.0 &  161.0 &  162.0 &  162.0 &  163.0 &  163 \\
CS                  &  159.646 &  1.005 &  155 &  158.0 &  159.0 &  160.0 &  160.0 &  161.0 &  161 \\
ZD-Extort-4         &  150.598 &  2.662 &  138 &  146.0 &  149.0 &  151.0 &  152.0 &  155.0 &  162 \\
Handshake           &  149.552 &  1.754 &  142 &  147.0 &  148.0 &  150.0 &  151.0 &  152.0 &  154 \\
ZD-Extort-2         &  146.094 &  3.445 &  129 &  140.0 &  144.0 &  146.0 &  148.0 &  152.0 &  160 \\
ZD-Extort-2 v2      &  146.291 &  3.425 &  131 &  141.0 &  144.0 &  146.0 &  149.0 &  152.0 &  160 \\
Winner21            &  139.946 &  1.225 &  136 &  138.0 &  139.0 &  140.0 &  141.0 &  142.0 &  143 \\
TF2                 &  138.240 &  1.700 &  130 &  135.0 &  137.0 &  138.0 &  139.0 &  141.0 &  143 \\
TF1                 &  135.692 &  1.408 &  130 &  133.0 &  135.0 &  136.0 &  137.0 &  138.0 &  140 \\
Naive Prober: 0.1   &  136.016 &  2.504 &  127 &  132.0 &  134.0 &  136.0 &  138.0 &  140.0 &  147 \\
Feld: 1.0, 0.5, 200 &  136.087 &  1.696 &  130 &  133.0 &  135.0 &  136.0 &  137.0 &  139.0 &  144 \\
Joss: 0.9           &  136.015 &  2.503 &  126 &  132.0 &  134.0 &  136.0 &  138.0 &  140.0 &  146 \\
Predator            &  133.718 &  1.385 &  129 &  131.0 &  133.0 &  134.0 &  135.0 &  136.0 &  138 \\
SolutionB5          &  125.843 &  1.509 &  120 &  123.0 &  125.0 &  126.0 &  127.0 &  128.0 &  131 \\
\bottomrule
\end{tabular}
\end{table}

\begin{landscape}
    \begin{figure}[!hbtp]
        \centering
        \includegraphics[width=\paperwidth]{standard_wins_boxplots.eps}
        \caption{\bf Standard Tournament: number of wins per tournament (ranked by
        median over
        50000 tournaments).}
        \label{fig:standard_winplot}
    \end{figure}
\end{landscape}

@@

\begin{table}[!hbtp]
    \caption{\bf Standard Tournament: Number of wins per tournament
        of top 15 strategies (ranked by median score over
        50000 tournaments).}
        \label{tbl:standard_wins}
    \centering
    \footnotesize
\begin{tabular}{lrrrrrrrrr}
\toprule
{} &    mean &    std &  min &    5\% &   25\% &   50\% &   75\% &   95\% &  max \\
\midrule
EvolvedLookerUp2\_2\_2$^{*}$    &  48.259 &  1.336 &   43 &  46.0 &  47.0 &  48.0 &  49.0 &  50.0 &   53 \\
Evolved HMM 5$^{*}$           &  41.358 &  1.221 &   36 &  39.0 &  41.0 &  41.0 &  42.0 &  43.0 &   45 \\
Evolved FSM 16$^{*}$          &  56.978 &  1.099 &   51 &  55.0 &  56.0 &  57.0 &  58.0 &  59.0 &   60 \\
PSO Gambler 2\_2\_2$^{*}$       &  40.692 &  1.089 &   36 &  39.0 &  40.0 &  41.0 &  41.0 &  42.0 &   45 \\
Evolved FSM 16 Noise 05$^{*}$ &  40.070 &  1.673 &   34 &  37.0 &  39.0 &  40.0 &  41.0 &  43.0 &   47 \\
PSO Gambler 1\_1\_1$^{*}$       &  45.005 &  1.595 &   38 &  42.0 &  44.0 &  45.0 &  46.0 &  48.0 &   51 \\
Evolved ANN 5$^{*}$           &  43.224 &  0.674 &   41 &  42.0 &  43.0 &  43.0 &  44.0 &  44.0 &   47 \\
Evolved FSM 4$^{*}$           &  37.227 &  0.951 &   34 &  36.0 &  37.0 &  37.0 &  38.0 &  39.0 &   41 \\
Evolved ANN$^{*}$             &  43.100 &  1.021 &   40 &  42.0 &  42.0 &  43.0 &  44.0 &  45.0 &   48 \\
PSO Gambler Mem1$^{*}$        &  43.444 &  1.837 &   34 &  40.0 &  42.0 &  43.0 &  45.0 &  46.0 &   51 \\
Evolved ANN 5 Noise 05$^{*}$  &  33.711 &  1.125 &   30 &  32.0 &  33.0 &  34.0 &  34.0 &  35.0 &   38 \\
DBS                           &  32.329 &  1.198 &   28 &  30.0 &  32.0 &  32.0 &  33.0 &  34.0 &   38 \\
Winner12                      &  40.179 &  1.037 &   36 &  39.0 &  39.0 &  40.0 &  41.0 &  42.0 &   44 \\
Fool Me Once                  &  50.121 &  0.422 &   48 &  50.0 &  50.0 &  50.0 &  50.0 &  51.0 &   52 \\
Omega TFT: 3, 8               &  35.157 &  0.859 &   32 &  34.0 &  35.0 &  35.0 &  36.0 &  37.0 &   39 \\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{table}[!hbtp]
    \centering
        \caption{\bf Standard Tournament: Rank in each tournament
        of top 15 strategies (ranked by median over
        50000 tournaments).}
    \footnotesize
\begin{tabular}{lrrrrrrrrr}
\toprule
{} &    mean &    std &  min &    5\% &   25\% &   50\% &   75\% &   95\% &  max \\
\midrule
EvolvedLookerUp2\_2\_2$^{*}$    &   2.173 &  1.070 &    1 &   1.0 &   1.0 &   2.0 &   3.0 &   4.0 &    8 \\
Evolved HMM 5$^{*}$           &   2.321 &  1.275 &    1 &   1.0 &   1.0 &   2.0 &   3.0 &   5.0 &   10 \\
Evolved FSM 16$^{*}$          &   2.489 &  1.299 &    1 &   1.0 &   1.0 &   2.0 &   3.0 &   5.0 &   10 \\
PSO Gambler 2\_2\_2$^{*}$       &   3.961 &  1.525 &    1 &   2.0 &   3.0 &   4.0 &   5.0 &   7.0 &   10 \\
Evolved FSM 16 Noise 05$^{*}$ &   6.300 &  1.688 &    1 &   4.0 &   5.0 &   6.0 &   7.0 &   9.0 &   11 \\
PSO Gambler 1\_1\_1$^{*}$       &   7.082 &  2.499 &    1 &   3.0 &   5.0 &   7.0 &   9.0 &  10.0 &   17 \\
Evolved ANN 5$^{*}$           &   7.287 &  1.523 &    2 &   5.0 &   6.0 &   7.0 &   8.0 &  10.0 &   11 \\
Evolved FSM 4$^{*}$           &   7.527 &  1.631 &    2 &   5.0 &   6.0 &   8.0 &   9.0 &  10.0 &   12 \\
Evolved ANN$^{*}$             &   7.901 &  1.450 &    2 &   5.0 &   7.0 &   8.0 &   9.0 &  10.0 &   12 \\
PSO Gambler Mem1$^{*}$        &   8.222 &  2.535 &    1 &   4.0 &   6.0 &   9.0 &  10.0 &  12.0 &   20 \\
Evolved ANN 5 Noise 05$^{*}$  &  11.362 &  0.872 &    8 &  10.0 &  11.0 &  11.0 &  12.0 &  13.0 &   16 \\
DBS                           &  12.197 &  1.125 &    9 &  11.0 &  11.0 &  12.0 &  13.0 &  14.0 &   16 \\
Winner12                      &  13.221 &  1.137 &    9 &  11.0 &  12.0 &  13.0 &  14.0 &  15.0 &   17 \\
Fool Me Once                  &  13.960 &  1.083 &    9 &  12.0 &  13.0 &  14.0 &  15.0 &  15.0 &   17 \\
Omega TFT: 3, 8               &  14.275 &  1.301 &    9 &  12.0 &  13.0 &  15.0 &  15.0 &  16.0 &   19 \\
\bottomrule
\end{tabular}
        \label{tbl:standard_ranks}
\end{table}

\begin{landscape}
    \begin{figure}[!hbtp]
        \centering
        \includegraphics[width=\paperwidth]{standard_ranks_boxplots.eps}
        \caption{\bf Standard Tournament: rank in each tournament (ranked by
        median over
        50000 tournaments).}
        \label{fig:standard_ranks_boxplot}
    \end{figure}
\end{landscape}

@@

\begin{figure}[!hbtp]
        \centering
        \includegraphics[width=.7\textwidth]{cooperation_0_0_10000_EvolvedLookerUp2_2_2_array.eps}
        \caption{\bf Cooperation rates for EvolvedLookerUp\_2\_2\_2
            (strategies ordered by median score over 10000 tournaments).}
        \label{fig:comparison_cooperation_heatmaps_standard_1}
\end{figure}

>>>>

% Header and Footer with logo
\usepackage{lastpage,fancyhdr}
\usepackage{graphicx}
\usepackage{epstopdf}
\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
\setlength{\headheight}{27.023pt}
\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\sf PLOS}

@@

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline
{ Reinforcement Learning Produces Dominant Strategies for the Iterated Prisoner's Dilemma }
% Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Marc Harper\textsuperscript{1\Yinyang},
Vincent Knight\textsuperscript{2*\Yinyang},
Martin Jones\textsuperscript{3\ddag},
Georgios Koutsovoulos\textsuperscript{4\ddag},
Nikoleta E. Glynatsi\textsuperscript{2\ddag},
Owen Campbell\textsuperscript{5\ddag},
\\
\bigskip
\textbf{1} Google Inc., Mountain View, CA, USA
\\
\textbf{2} Cardiff University, School of Mathematics, UK
\\
\textbf{3} Python for biologist (\url{https://pythonforbiologists.com})
\\
\textbf{4} INRA, Université Côte d‘Azur, CNRS, ISA, France
\\
\textbf{5} Axelrod-Python Project
\\
\bigskip

@@

\begin{figure}[!hbtp]
    \centering
    %\includegraphics[width=.7\textwidth]{lookerup.eps}
    \caption{\bf Diagrammatic representation of the Looker up Archetype.}
    \label{fig:lookerup}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    %\includegraphics[width=.7\textwidth]{gambler.eps}
    \caption{\bf Diagrammatic representation of the Gambler Archetype.}
    \label{fig:gambler}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    %\includegraphics[width=.9\textwidth]{ann.eps}
    \caption{\bf Diagrammatic representation of the ANN Archetype.}
    \label{fig:ann}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    %\includegraphics[width=\textwidth]{fsm.eps}
    \caption{\bf Diagrammatic representation of the Finite State Machine Archetype.}
    \label{fig:fsm}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    %\includegraphics[width=.5\textwidth]{FSM16.eps}
        \caption{\bf Evolved\_FSM\_16: trained to maximize score in a standard
        tournament}
        \label{fig:fsm16}
\end{figure}

\begin{figure}
        \centering
        %\includegraphics[width=.5\textwidth]{FSM16noise.eps}
        \caption{\bf Evolved\_FSM\_16\_Noise\_05: trained to maximize score in a
        noisy tournament}
        \label{fig:fsm16noise}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    %\includegraphics[width=\textwidth]{hmm.eps}
    \caption{\bf Diagrammatic representation of the Hidden Markov Model Archetype.}
    \label{fig:hmm}
\end{figure}

@@

\begin{figure}[!hbtp]
        \centering
        %\includegraphics[width=.5\textwidth]{standard_tft_scores.eps}
        \caption{\bf Scores for Tit for Tat over
        50000 tournaments.}
        \label{fig:tit_for_tat_scores}
\end{figure}

\begin{figure}[!hbtp]
        \centering
        %\includegraphics[width=.5\textwidth]{standard_tft_ranks.eps}
        \caption{\bf Ranks for Tit for Tat over
        50000 tournaments.}
        \label{fig:tit_for_tat_ranks}
\end{figure}

\begin{figure}[!hbtp]
        \centering
        %\includegraphics[width=.5\textwidth]{standard_tft_wins.eps}
        \caption{\bf Wins for Tit for Tat over
        50000 tournaments.}
        \label{fig:tit_for_tat_wins}
\end{figure}

@@

\begin{table}[!hbtp]
        \centering
        \footnotesize
        \caption{\bf Standard Tournament: Mean score per turn of top 15 strategies
            (ranked by median over 50000 tournaments).
        The leaderboard is dominated by the trained strategies (indicated by a
        $^{*}$).}
\begin{tabular}{lrrrrrrrrr}
\toprule
{} &   mean &    std &    min &     5\% &    25\% &    50\% &    75\% &    95\% &    max \\
\midrule
EvolvedLookerUp2\_2\_2$^{*}$    &  2.955 &  0.010 &  2.915 &  2.937 &  2.948 &  2.956 &  2.963 &  2.971 &  2.989 \\
Evolved HMM 5$^{*}$           &  2.954 &  0.014 &  2.903 &  2.931 &  2.945 &  2.954 &  2.964 &  2.977 &  3.007 \\
Evolved FSM 16$^{*}$          &  2.952 &  0.013 &  2.900 &  2.930 &  2.943 &  2.953 &  2.962 &  2.973 &  2.993 \\
PSO Gambler 2\_2\_2$^{*}$       &  2.938 &  0.013 &  2.884 &  2.914 &  2.930 &  2.940 &  2.948 &  2.957 &  2.972 \\
Evolved FSM 16 Noise 05$^{*}$ &  2.919 &  0.013 &  2.874 &  2.898 &  2.910 &  2.919 &  2.928 &  2.939 &  2.965 \\
PSO Gambler 1\_1\_1$^{*}$       &  2.912 &  0.023 &  2.805 &  2.874 &  2.896 &  2.912 &  2.928 &  2.950 &  3.012 \\
Evolved ANN 5$^{*}$           &  2.912 &  0.010 &  2.871 &  2.894 &  2.905 &  2.912 &  2.919 &  2.928 &  2.945 \\
Evolved FSM 4$^{*}$           &  2.910 &  0.012 &  2.867 &  2.889 &  2.901 &  2.910 &  2.918 &  2.929 &  2.943 \\
Evolved ANN$^{*}$             &  2.907 &  0.010 &  2.865 &  2.890 &  2.900 &  2.908 &  2.914 &  2.923 &  2.942 \\
PSO Gambler Mem1$^{*}$        &  2.901 &  0.025 &  2.783 &  2.858 &  2.884 &  2.901 &  2.919 &  2.942 &  2.994 \\
Evolved ANN 5 Noise 05$^{*}$  &  2.864 &  0.008 &  2.830 &  2.850 &  2.858 &  2.865 &  2.870 &  2.877 &  2.891 \\
DBS                           &  2.857 &  0.009 &  2.823 &  2.842 &  2.851 &  2.857 &  2.863 &  2.872 &  2.899 \\
Winner12                      &  2.849 &  0.008 &  2.820 &  2.836 &  2.844 &  2.850 &  2.855 &  2.862 &  2.874 \\
Fool Me Once                  &  2.844 &  0.008 &  2.818 &  2.830 &  2.838 &  2.844 &  2.850 &  2.857 &  2.882 \\
Omega TFT: 3, 8               &  2.841 &  0.011 &  2.800 &  2.822 &  2.833 &  2.841 &  2.849 &  2.859 &  2.882 \\
\bottomrule
\end{tabular}
        \label{tbl:standard_score}
\end{table}

@@

\begin{figure}[!hbtp]
    \centering
    %\includegraphics[width=\paperwidth]{standard_scores_boxplots.eps}
    \caption{\bf Standard Tournament: Mean score per turn 
        (strategies ordered by median score over 50000 tournaments).}
    \label{fig:standard_boxplot}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    %\includegraphics[width=\textwidth]{standard_scores_heatmap.eps}
    \caption{\bf Standard Tournament: Mean score per turn of row players against
    column players (ranked by median over 50000 tournaments).}
    \label{fig:standard_heatmap}
\end{figure}

@@

\begin{table}[!hbtp]
    \centering
        \caption{\bf Standard Tournament: Number of wins per tournament
        of top 15 strategies (ranked by median wins over
        50000 tournaments). }
        \label{tbl:standard_wins_top_winners}
\begin{tabular}{lrrrrrrrrr}
\toprule
{} &     mean &    std &  min &     5\% &    25\% &    50\% &    75\% &    95\% &  max \\
\midrule
Aggravater          &  161.595 &  0.862 &  160 &  160.0 &  161.0 &  162.0 &  162.0 &  163.0 &  163 \\
Defector            &  161.605 &  0.864 &  160 &  160.0 &  161.0 &  162.0 &  162.0 &  163.0 &  163 \\
CS                  &  159.646 &  1.005 &  155 &  158.0 &  159.0 &  160.0 &  160.0 &  161.0 &  161 \\
ZD-Extort-4         &  150.598 &  2.662 &  138 &  146.0 &  149.0 &  151.0 &  152.0 &  155.0 &  162 \\
Handshake           &  149.552 &  1.754 &  142 &  147.0 &  148.0 &  150.0 &  151.0 &  152.0 &  154 \\
ZD-Extort-2         &  146.094 &  3.445 &  129 &  140.0 &  144.0 &  146.0 &  148.0 &  152.0 &  160 \\
ZD-Extort-2 v2      &  146.291 &  3.425 &  131 &  141.0 &  144.0 &  146.0 &  149.0 &  152.0 &  160 \\
Winner21            &  139.946 &  1.225 &  136 &  138.0 &  139.0 &  140.0 &  141.0 &  142.0 &  143 \\
TF2                 &  138.240 &  1.700 &  130 &  135.0 &  137.0 &  138.0 &  139.0 &  141.0 &  143 \\
TF1                 &  135.692 &  1.408 &  130 &  133.0 &  135.0 &  136.0 &  137.0 &  138.0 &  140 \\
Naive Prober: 0.1   &  136.016 &  2.504 &  127 &  132.0 &  134.0 &  136.0 &  138.0 &  140.0 &  147 \\
Feld: 1.0, 0.5, 200 &  136.087 &  1.696 &  130 &  133.0 &  135.0 &  136.0 &  137.0 &  139.0 &  144 \\
Joss: 0.9           &  136.015 &  2.503 &  126 &  132.0 &  134.0 &  136.0 &  138.0 &  140.0 &  146 \\
Predator            &  133.718 &  1.385 &  129 &  131.0 &  133.0 &  134.0 &  135.0 &  136.0 &  138 \\
SolutionB5          &  125.843 &  1.509 &  120 &  123.0 &  125.0 &  126.0 &  127.0 &  128.0 &  131 \\
\bottomrule
\end{tabular}
\end{table}

\begin{figure}[!hbtp]
    \centering
    %\includegraphics[width=\paperwidth]{standard_wins_boxplots.eps}
    \caption{\bf Standard Tournament: number of wins per tournament (ranked by
    median over
    50000 tournaments).}
    \label{fig:standard_winplot}
\end{figure}

@@

\begin{table}[!hbtp]
    \caption{\bf Standard Tournament: Number of wins per tournament
        of top 15 strategies (ranked by median score over
        50000 tournaments)
        ~$^{*}$ indicates that the strategy was trained.}
        \label{tbl:standard_wins}
    \centering
    \footnotesize
\begin{tabular}{lrrrrrrrrr}
\toprule
{} &    mean &    std &  min &    5\% &   25\% &   50\% &   75\% &   95\% &  max \\
\midrule
EvolvedLookerUp2\_2\_2$^{*}$    &  48.259 &  1.336 &   43 &  46.0 &  47.0 &  48.0 &  49.0 &  50.0 &   53 \\
Evolved HMM 5$^{*}$           &  41.358 &  1.221 &   36 &  39.0 &  41.0 &  41.0 &  42.0 &  43.0 &   45 \\
Evolved FSM 16$^{*}$          &  56.978 &  1.099 &   51 &  55.0 &  56.0 &  57.0 &  58.0 &  59.0 &   60 \\
PSO Gambler 2\_2\_2$^{*}$       &  40.692 &  1.089 &   36 &  39.0 &  40.0 &  41.0 &  41.0 &  42.0 &   45 \\
Evolved FSM 16 Noise 05$^{*}$ &  40.070 &  1.673 &   34 &  37.0 &  39.0 &  40.0 &  41.0 &  43.0 &   47 \\
PSO Gambler 1\_1\_1$^{*}$       &  45.005 &  1.595 &   38 &  42.0 &  44.0 &  45.0 &  46.0 &  48.0 &   51 \\
Evolved ANN 5$^{*}$           &  43.224 &  0.674 &   41 &  42.0 &  43.0 &  43.0 &  44.0 &  44.0 &   47 \\
Evolved FSM 4$^{*}$           &  37.227 &  0.951 &   34 &  36.0 &  37.0 &  37.0 &  38.0 &  39.0 &   41 \\
Evolved ANN$^{*}$             &  43.100 &  1.021 &   40 &  42.0 &  42.0 &  43.0 &  44.0 &  45.0 &   48 \\
PSO Gambler Mem1$^{*}$        &  43.444 &  1.837 &   34 &  40.0 &  42.0 &  43.0 &  45.0 &  46.0 &   51 \\
Evolved ANN 5 Noise 05$^{*}$  &  33.711 &  1.125 &   30 &  32.0 &  33.0 &  34.0 &  34.0 &  35.0 &   38 \\
DBS                           &  32.329 &  1.198 &   28 &  30.0 &  32.0 &  32.0 &  33.0 &  34.0 &   38 \\
Winner12                      &  40.179 &  1.037 &   36 &  39.0 &  39.0 &  40.0 &  41.0 &  42.0 &   44 \\
Fool Me Once                  &  50.121 &  0.422 &   48 &  50.0 &  50.0 &  50.0 &  50.0 &  51.0 &   52 \\
Omega TFT: 3, 8               &  35.157 &  0.859 &   32 &  34.0 &  35.0 &  35.0 &  36.0 &  37.0 &   39 \\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{table}[!hbtp]
    \centering
        \caption{\bf Standard Tournament: Rank in each tournament
        of top 15 strategies (ranked by median over
        50000 tournaments)
        ~$^{*}$ indicates that the strategy was trained.}
    \footnotesize
\begin{tabular}{lrrrrrrrrr}
\toprule
{} &    mean &    std &  min &    5\% &   25\% &   50\% &   75\% &   95\% &  max \\
\midrule
EvolvedLookerUp2\_2\_2$^{*}$    &   2.173 &  1.070 &    1 &   1.0 &   1.0 &   2.0 &   3.0 &   4.0 &    8 \\
Evolved HMM 5$^{*}$           &   2.321 &  1.275 &    1 &   1.0 &   1.0 &   2.0 &   3.0 &   5.0 &   10 \\
Evolved FSM 16$^{*}$          &   2.489 &  1.299 &    1 &   1.0 &   1.0 &   2.0 &   3.0 &   5.0 &   10 \\
PSO Gambler 2\_2\_2$^{*}$       &   3.961 &  1.525 &    1 &   2.0 &   3.0 &   4.0 &   5.0 &   7.0 &   10 \\
Evolved FSM 16 Noise 05$^{*}$ &   6.300 &  1.688 &    1 &   4.0 &   5.0 &   6.0 &   7.0 &   9.0 &   11 \\
PSO Gambler 1\_1\_1$^{*}$       &   7.082 &  2.499 &    1 &   3.0 &   5.0 &   7.0 &   9.0 &  10.0 &   17 \\
Evolved ANN 5$^{*}$           &   7.287 &  1.523 &    2 &   5.0 &   6.0 &   7.0 &   8.0 &  10.0 &   11 \\
Evolved FSM 4$^{*}$           &   7.527 &  1.631 &    2 &   5.0 &   6.0 &   8.0 &   9.0 &  10.0 &   12 \\
Evolved ANN$^{*}$             &   7.901 &  1.450 &    2 &   5.0 &   7.0 &   8.0 &   9.0 &  10.0 &   12 \\
PSO Gambler Mem1$^{*}$        &   8.222 &  2.535 &    1 &   4.0 &   6.0 &   9.0 &  10.0 &  12.0 &   20 \\
Evolved ANN 5 Noise 05$^{*}$  &  11.362 &  0.872 &    8 &  10.0 &  11.0 &  11.0 &  12.0 &  13.0 &   16 \\
DBS                           &  12.197 &  1.125 &    9 &  11.0 &  11.0 &  12.0 &  13.0 &  14.0 &   16 \\
Winner12                      &  13.221 &  1.137 &    9 &  11.0 &  12.0 &  13.0 &  14.0 &  15.0 &   17 \\
Fool Me Once                  &  13.960 &  1.083 &    9 &  12.0 &  13.0 &  14.0 &  15.0 &  15.0 &   17 \\
Omega TFT: 3, 8               &  14.275 &  1.301 &    9 &  12.0 &  13.0 &  15.0 &  15.0 &  16.0 &   19 \\
\bottomrule
\end{tabular}
        \label{tbl:standard_ranks}
\end{table}

\begin{figure}[!hbtp]
    \centering
    %\includegraphics[width=\paperwidth]{standard_ranks_boxplots.eps}
    \caption{\bf Standard Tournament: rank in each tournament (ranked by
    median over
    50000 tournaments).}
    \label{fig:standard_ranks_boxplot}
\end{figure}

@@

\begin{figure}[!hbtp]
        \centering
        %\includegraphics[width=.7\textwidth]{cooperation_0_0_10000_EvolvedLookerUp2_2_2_array.eps}
        \caption{\bf Cooperation rates for EvolvedLookerUp\_2\_2\_2
            (strategies ordered by median score over 10000 tournaments).}
        \label{fig:comparison_cooperation_heatmaps_standard_1}
\end{figure}

\begin{figure}[!hbtp]
        \centering
        %\includegraphics[width=.7\textwidth]{cooperation_0_0_10000_Evolved_HMM_5_array.eps}
        \caption{\bf Cooperation rates for Evolved\_HMM\_5
            (strategies ordered by median score over 10000 tournaments).}
        \label{fig:comparison_cooperation_heatmaps_standard_2}
\end{figure}
